---
title: "chapter3"
author: "Wenhui Zeng"
date: "Feb 9th 2016"
output: pdf_document
---
##1 
The null hypothesis for "TV" is that in the presence of radio ads and newspaper ads, TV ads have no effect on sales. Similarly, the null hypothesis for "radio" is that in the presence of TV and newspaper ads, radio ads have no effect on sales. (And there is a similar null hypothesis for
"newspaper".) The low p-values of TV and radio suggest that the null hypotheses are false for TV and radio. The high p-value of newspaper suggests that the null hypothesis is true for newspaper.

##2
KNN classifier and KNN regression methods are closely related in formula. However, the final result of KNN classifier is the classification output for Y (qualitative), whereas the output for a KNN regression predicts the quantitative value for f(X).

##3 
###i

Incorrect

###ii

Correct

###iii

Correct

###iv

Incorrect

Male=50+GPA*20+IQ*0.07+0.01*GPA*IQ
Female =50+ GPA*20+IQ*0.07+0.01*GPA*IQ+35-10*GPA
B: 137.1
C: False. We must examine the p-value of the regression coefficient to
determine if the interaction term is statistically significant or not.

##4
###(a)
I would expect the polynomial regression to have a lower training RSS
than the linear regression because it could make a tighter fit against data that
matched with a wider irreducible error (Var(epsilon)).

###(b) 

I would expect the polynomial regression to have a higher test RSS as the overfit from training would have more error than the linear regression.

###(c) 

Polynomial regression has lower train RSS than the linear fit because of higher flexibility: no matter what the underlying true relationship is the more flexible model will closer follow points and reduce train RSS. An example of this behavior is shown on Figure~2.9 from Chapter

###(d)

There is not enough information to tell which test RSS would be lower for either regression given the problem statement is defined as not knowing "how far it is from linear". If it is closer to linear than cubic, the linear regression test RSS could be lower than the cubic regression test RSS. Or, if it is closer to cubic than linear, the cubic regression test RSS could be lower than the linear regression test RSS. It is dues to bias-variance tradeoff: it is not clear what level of flexibility will fit data better.

##5
$$\hat{y_i} =x_i\hat{\beta_i} $$
$$\hat{\beta}=\sum_{i=1}^{n}y_ix_i$$
$$\hat{y_i}=\frac{x_i\sum_{i=1}^{n}x_i'y_i'}{\sum_{i=1}^{k}x_k^2}=\sum_{i=1}^{k}\frac{x_i'y_i'}{\sum_{i=1}^{k}x_l^2}y_i'$$
$$a=\frac{x_i'x_i}{\sum_{i=1}^{k}x_k^2}$$
##6-7
$$y = \beta_0 +\beta_1 x$$
$$\beta_0 = avg(y) - \beta_1 avg(x)$$
right hand side will equal 0 if (avg(x), avg(y)) is a point on the line
$$0 = (avg(y) - \beta_0 avg(x)) + \beta_1 avg(x) - avg(y)$$

##8
###a
```{r,echo=F,warning=F}
library(ISLR)
Auto <- na.omit(Auto)
lm.fit <- lm(mpg ~ horsepower,data=Auto)
lm.fit2<-summary(lm.fit)
f <- round(lm.fit2$fstatistic[1], 2)
df1 <- lm.fit2$fstatistic[2]
df2 <- lm.fit2$fstatistic[3]
p <- signif(pf(f, df1, df2, lower.tail = F), 2)
r2 <- round(lm.fit2$r.squared, 2)
attributes(p) <- NULL 
```

####i.
Yes, there is a relationship between horsepower and mpg as deterined by testing the null hypothesis of all regression coefficients equal to zero. Since the F-statistic is far larger than 1 and the p-value of the F-statistic is close to zero we can reject the null hypothesis and state there is a statistically significant relationship between horsepower and mpg.

####ii.
To calculate the residual error relative to the response we use the mean of the response and the RSE. The mean of mpg is r mean(mpg, na.rm=T). The RSE of the lm.fit was r 4.906 which indicates a percentage error of r 4.906/mean(mpg, na.rm=T).100.0% of the variance in mpg is explained by horsepower.

The relationship between mpg and horsepower is negative. The more horsepower an automobile has the linear regression indicates the less mpg fuel efficiency the automobile will have.

####iv.
```{r,echo=F,warning=F}
p1<-predict(lm.fit, data.frame(horsepower=c(98)), interval="confidence")
p2<-predict(lm.fit, data.frame(horsepower=c(98)), interval="prediction")
```
The prediction confidence interval is `r p1` and the prediction interval is `r p2`

###b.
```{r,echo=F,warning=F}
with(Auto,plot(horsepower, mpg))
abline(lm.fit)
```


###c.
```{r,,echo=F,warning=F}
par(mfrow=c(2,2))
plot(lm.fit)
```
Based on the residuals plots, there is some evidence of non-linearity.

##9
###a
```{r,,echo=F,warning=F}
pairs(Auto)
```

###b
```{r,,echo=F,warning=F}
cor(subset(Auto, select=-name))
```

###c
```{r,,echo=F,warning=F}
lm.fit1 <- lm(mpg~.-name, data=Auto)
summary(lm.fit1)
```


##9
###d.
```{r,,echo=F,warning=F}
par(mfrow=c(2,2))
plot(lm.fit1)
```
The fit does not appear to be accurate because there is a discernible curve pattern to the residuals plots. From the leverage plot, point 14 appears to have high leverage, although not a high magnitude residual.

plot(predict(lm.fit1), rstudent(lm.fit1))
There are possible outliers as seen in the plot of studentized residuals because there are data with a value greater than 3.

###e.
```{r,,echo=F,warning=F}
lm.fit2 <- lm(mpg~cylinders*displacement+displacement*weight,data=Auto)
summary(lm.fit2)
```
From the correlation matrix, I obtained the two highest correlated pairs and used them in picking my interaction effects. From the p-values, we can see that the interaction between displacement and weight is statistically signifcant, while the interactiion between cylinders and displacement is not.

###f.
```{r,,echo=F,warning=F}
lm.fit3 <- lm(mpg~log(weight)+sqrt(horsepower)+acceleration+I(acceleration^2),data=Auto)
summary(lm.fit3)
par(mfrow=c(2,2))
plot(lm.fit3)
plot(predict(lm.fit3), rstudent(lm.fit3))
```
Apparently, from the p-values, the log(weight), sqrt(horsepower), and acceleration^2 all have statistical significance of some sort. The residuals plot has less of a discernible pattern than the plot of all linear regression terms. The studentized residuals displays potential outliers (>3). The leverage plot indicates more than three points with high leverage.

However, 2 problems are observed from the above plots: 1) the residuals vs fitted plot indicates heteroskedasticity (unconstant variance over mean) in the model. 2) The Q-Q plot indicates somewhat unnormality of the residuals.

So, a better transformation need to be applied to our model. From the correlation matrix in 9a., displacement, horsepower and weight show a similar nonlinear pattern against our response mpg. This nonlinear pattern is very close to a log form. So in the next attempt, we use log(mpg) as our response variable.

The outputs show that log transform of mpg yield better model fitting (better R^2, normality of residuals).
```{r,,echo=F,warning=F}
lm.fit2<-lm(log(mpg)~cylinders+displacement+horsepower+weight+acceleration+year+origin,data=Auto)
summary(lm.fit2)
par(mfrow=c(2,2)) 
plot(lm.fit2)
plot(predict(lm.fit2),rstudent(lm.fit2))
```

##10
###a
```{r,,echo=F,warning=F}
library(ISLR)
lm.fit = lm(Sales~Price+Urban+US,data=Carseats)
summary(lm.fit)
```

###b
Price
The linear regression suggests a relationship between price and sales given the low p-value of the t-statistic. The coefficient states a negative relationship between Price and Sales: as Price increases, Sales decreases.

UrbanYes
The linear regression suggests that there isn't a relationship between the location of the store and the number of sales based on the high p-value of the t-statistic.

USYes
The linear regression suggests there is a relationship between whether the store is in the US or not and the amount of sales. The coefficient states a positive relationship between USYes and Sales: if the store is in the US, the sales will increase by approximately 1201 units.

###c.
Sales = 13.04 + -0.05 Price + -0.02 UrbanYes + 1.20 USYes

###d.

Price and USYes, based on the p-values, F-statistic, and p-value of the F-statistic.

###e.
```{r,echo=F,warning=F}
lm.fit2 <- lm(Sales ~ Price + US,data=Carseats)
summary(lm.fit2)
```

###f.
Based on the RSE and R^2 of the linear regressions, they both fit the data similarly, with linear regression from (e) fitting the data slightly better.

###g.
```{r,echo=F,warning=F}
a<-confint(lm.fit2)
```

###h.
```{r,echo=F,warning=F}
plot(predict(lm.fit2), rstudent(lm.fit2))
```
All studentized residuals appear to be bounded by -3 to 3, so not potential outliers are suggested from the linear regression.
```{r,echo=F,warning=F}
par(mfrow=c(2,2))
plot(lm.fit2)
```
There are a few observations that greatly exceed  `r 3/397` on the leverage-statistic plot that suggest that the corresponding points have high leverage.


##11.
###a
```{r,echo=F,warning=F}
set.seed(1)
x = rnorm(100)
y = 2*x + rnorm(100)

lm.fit <- lm(y~x+0)
summary(lm.fit)
```
The p-value of the t-statistic is near zero so the null hypothesis is rejected.

###b.
```{r,echo=F,warning=F}
lm.fit <- lm(x~y+0)
summary(lm.fit)
```
The p-value of the t-statistic is near zero so the null hypothesis is rejected.

###c.
Both results in (a) and (b) reflect the same line created in 11a. In other words, $y = 2x + \epsilon$ could also be written $x = 0.5 * (y - \epsilon)$.

###d.

$$t = \beta / SE(\beta) $$
$$\beta = \frac {\sum{x_i y_i}} {\sum{x_i^2}}$$
$$SE(\beta) =\sqrt{\frac {\sum{(y_i - x_i \beta)^2}} {(n-1) \sum{x_i^2}}} $$
$$\ t = {\frac {\sum{x_i y_i}} {\sum{x_i^2}}} {\sqrt{\frac {(n-1) \sum{x_i^2}} {\sum{(y_i - x_i \beta)^2}}}} \ \frac {\sqrt{n-1} \sum{x_i y_i}} {\sqrt{\sum{x_i^2} \sum{(y_i - x_i \beta)^2}}} \ \frac {\sqrt{n-1} \sum{x_i y_i}} {\sqrt{\sum{x_i^2} \sum{(y_i^2 - 2 \beta x_i y_i + x_i^2 \beta^2)}}} \ \frac {\sqrt{n-1} \sum{x_i y_i}} {\sqrt{\sum{x_i^2} \sum{y_i^2} - \sum{x_i^2} \beta (2 \sum{x_i y_i} - \beta \sum{x_i^2})}} \ \frac {\sqrt{n-1} \sum{x_i y_i}} {\sqrt{\sum{x_i^2} \sum{y_i^2} - \sum{x_i y_i} (2 \sum{x_i y_i} - \sum{x_i y_i})}} $$
$$\ t = \frac {\sqrt{n-1} \sum{x_i y_i}} {\sqrt{\sum{x_i^2} \sum{y_i^2} - (\sum{x_i y_i})^2 }}$$


(sqrt(length(x)-1) * sum(x*y)) / (sqrt(sum(x*x) * sum(y*y) - (sum(x*y))^2))
This is same as the t-statistic shown above.

###e.

If you swap t(x,y) as t(y,x), then you will find t(x,y) = t(y,x).

###f.
```{r,echo=F,warning=F}
lm.fit <- lm(y~x)
lm.fit2 <- lm(x~y)
summary(lm.fit)
summary(lm.fit2)
```
You can see the t-statistic is the same for the two linear regressions.

##12

###a.

When the sum of the squares of the observed y-values are equal to the sum of the squares of the observed x-values.

##12

###b.
```{r,echo=F,warning=F}
set.seed(1)
x <- rnorm(100)
y <- 2*x
lm.fit <- lm(y~x+0)
lm.fit2 <- lm(x~y+0)
summary(lm.fit)
summary(lm.fit2)
```
The regression coefficients are different for each linear regression.


###c.
```{r,echo=F,warning=F}
set.seed(1)
x <- rnorm(100)
y <- -sample(x, 100)
sum(x^2)
sum(y^2)
lm.fit <- lm(y~x+0)
lm.fit2 <- lm(x~y+0)
summary(lm.fit)
summary(lm.fit2)
```
The regression coefficients are the same for each linear regression. So long as sum sum(x^2) = sum(y^2) the condition in 12a. will be satisfied. Here we have simply taken all the $x_i$ in a different order and made them negative.

##13
###a.
```{r,echo=F,warning=F}
set.seed(1)
x = rnorm(100)
```

###b.
```{r,echo=F,warning=F}
eps = rnorm(100, 0, sqrt(0.25))
```

###c.
```{r,echo=F,warning=F}
y = -1 + 0.5*x + eps
```
y is of length 100. $\beta_0$ is -1, $\beta_1$ is 0.5.

###d.
```{r,echo=F,warning=F}
plot(x, y)
```
I observe a linear relationship between x and y with a positive slope, with a variance as is to be expected.

###e.
```{r,echo=F,warning=F}
lm.fit <- lm(y~x)
summary(lm.fit)
```
The linear regression fits a model close to the true value of the coefficients as was constructed. The model has a large F-statistic with a near-zero p-value so the null hypothesis can be rejected.

###f.
```{r,echo=F,warning=F}
plot(x, y)
abline(lm.fit, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
```

###g.
```{r,echo=F,warning=F}
lm.fit_sq <- lm(y~x+I(x^2))
summary(lm.fit_sq)
```
There is evidence that model fit has increased over the training data given the slight increase in $R^2$ and $RSE$. Although, the p-value of the t-statistic suggests that there isn't a relationship between y and $x^2$.

###h.
```{r,echo=F,warning=F}
set.seed(1)
eps1 = rnorm(100, 0, 0.125)
x1 = rnorm(100)
y1 = -1 + 0.5*x1 + eps1
plot(x1, y1)
lm.fit1 = lm(y1~x1)
summary(lm.fit1)
abline(lm.fit1, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
```
As expected, the error observed in $R^2$ and $RSE$ decreases considerably.

###i.
```{r,echo=F,warning=F}
set.seed(1)
eps2 = rnorm(100, 0, 0.5)
x2 = rnorm(100)
y2 = -1 + 0.5*x2 + eps2
plot(x2, y2)
lm.fit2 = lm(y2~x2)
summary(lm.fit2)
abline(lm.fit2, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=3)
```
As expected, the error observed in $R^2$ and $RSE$ increases considerably.

###j.
```{r,echo=F,warning=F}
confint(lm.fit)
confint(lm.fit1)
confint(lm.fit2)
```
All intervals seem to be centered on approximately 0.5, with the second fit's interval being narrower than the first fit's interval and the last fit's interval being wider than the first fit's interval.

##14

###a.
```{r,echo=F,warning=F}
set.seed(1)
x1 = runif(100)
x2 = 0.5 * x1 + rnorm(100)/10
y = 2 + 2*x1 + 0.3*x2 + rnorm(100)
```
$$ Y = 2 + 2 X_1 + 0.3 X_2 + \epsilon \ \beta_0 = 2, \beta_1 = 2, \beta_3 = 0.3 $$

###b.
```{r,echo=F,warning=F}
cor(x1, x2)
plot(x1, x2)
```

###c
```{r,echo=F,warning=F}
lm.fit <- lm(y~x1+x2)
summary(lm.fit)
```
$$\beta_0 = 2.0533, \beta_1 = 1.6336, \beta_3 = 0.5588$$ The regression coefficients are close to the true coefficients, although with high standard error. We can reject the null hypothesis for $\beta_1$ because its p-value is below 5%. We cannot reject the null hypothesis for $\beta_2$ because its p-value is much above the 5% typical cutoff, over 60%.

###d.
```{r,echo=F,warning=F}
lm.fit <- lm(y~x1)
summary(lm.fit)
```
Yes, we can reject the null hypothesis for the regression coefficient given the p-value for its t-statistic is near zero.

###e.
```{r,echo=F,warning=F}
lm.fit <- lm(y~x2)
summary(lm.fit)
```
Yes, we can reject the null hypothesis for the regression coefficient given the p-value for its t-statistic is near zero.

###f.

No, because x1 and x2 have collinearity, it is hard to distinguish their effects when regressed upon together. When they are regressed upon separately, the linear relationship between y and each predictor is indicated more clearly.

###g.
```{r,echo=F,warning=F}
x1 = c(x1, 0.1)
x2 = c(x2, 0.8)
y = c(y, 6)
lm.fit1 = lm(y~x1+x2)
summary(lm.fit1)
lm.fit2 = lm(y~x1)
summary(lm.fit2)
lm.fit3 = lm(y~x2)
summary(lm.fit3)
```
In the first model, it shifts x1 to statistically insignificance and shifts x2 to statistiscal significance from the change in p-values between the two linear regressions.

```{r,echo=F,warning=F}
par(mfrow=c(2,2))
plot(lm.fit1)
par(mfrow=c(2,2))
plot(lm.fit2)
par(mfrow=c(2,2))
plot(lm.fit3)
```
In the first and third models, the point becomes a high leverage point.

```{r,echo=F,warning=F}
plot(predict(lm.fit1), rstudent(lm.fit1))
plot(predict(lm.fit2), rstudent(lm.fit2))
plot(predict(lm.fit3), rstudent(lm.fit3))
```
Looking at the studentized residuals, we don't observe points too far from the |3| value cutoff, except for the second linear regression: y ~ x1.






