---
title: "Chapter9"
author: "Wenhui Zeng"
date: "February 14, 2017"
output: pdf_document
---


#1

```{r,echo=F,warning=F}
x1<--10:10
x2=3*x1-1
plot(x1,x2,type="l",col="red")
text(c(-1),c(15), labels = c("Greater than 0"), col = "blue")
text(c(1),c(-15), labels = c("Less than 0"), col = "blue")
#Add Connected Line Segments to a Plot
lines(x1,-1/2*x1+1)
text(c(0),c(-8), labels = c("Less than 0"))
text(c(3),c(20), labels = c("Greater than 0"))
```

#2

##a-b
```{r,echo=F,warning=F}
radius = 2
plot(NA, NA, type = "n", xlim = c(-4, 2), ylim = c(-1, 5), asp = 1, xlab = "X1", 
     ylab = "X2")
#if add is TRUE, the symbols are added to an existing plot, otherwise a new plot is created.
#inches is FALSE, the units are taken to be those of the appropriate axes. 
symbols(c(-1), c(2), circles = c(radius), add = TRUE, inches = FALSE)
text(c(-1),c(2), labels = c("< 4"))
text(c(-3),c(4), labels = c("> 4"))
```

##c
(-1,1) belong to red, 
(2,2) belong to blue,
(0,0) belong to blue,
(3,8) belong to blue

##d
$(1+x_1)^2+(2-x_2)^2>4$ is $1+2 x_1+x_1^2+4-4 x_2+x_2^2>4 = 5+2  x_1+x_1^2-4x_2+x_2^2>4$ It is linear iterms of $x_1,x_1^2,x_2,x-2^2$

#3

##a-b
The hyperplane woubld be betwen the observation #2, #3,#5,#6
(2,2),(4,4)(blue) (2,1),(4,3)(red)
The line between them is (2,1.5) and (4,3.5)
slop=(3.5-1.5)/(4-2)=1
intercept=1.5-2=-.5

```{r,echo=F,warning=F}
x1<-c(3,2,4,1,2,4,4)
x2<-c(4,2,4,4,1,3,1)
cols<-c("red","red","red","red","Blue","Blue","Blue")
plot(x1,x2,col=cols,xlim = c(-1,5),ylim =c(-1,5) )
abline(-0.5,1)
```

##c
The equation is
$$0.5-x_1+x_2>0$$ 
$\beta_0$ is 0.5, $\beta_1$ is -1 $\beta_2$ is 1

##d
```{r,echo=F,warning=F}
x1<-c(3,2,4,1,2,4,4)
x2<-c(4,2,4,4,1,3,1)
cols<-c("red","red","red","red","Blue","Blue","Blue")
plot(x1,x2,col=cols,xlim = c(-1,5),ylim =c(-1,5) )
abline(-0.5, 1)
abline(-1, 1, lty = 2,col="Red")
abline(0, 1, lty = 2,col="Red")
```

#e
support vectors are observations  #2, #3,#5,#6

#f

Because #7 observation is out of the margin, it will not affect the maximal margin hyperplane

#g

```{r,echo=F,warning=F}
x1<-c(3,2,4,1,2,4,4)
x2<-c(4,2,4,4,1,3,1)
cols<-c("red","red","red","red","Blue","Blue","Blue")
plot(x1,x2,col=cols,xlim = c(-1,5),ylim =c(-1,5) )
abline(-0.6, 1.1)
```

The equation is
$$0.6-1.1x_1+x_2>0$$ 
#h
```{r,echo=F,warning=F}
x1<-c(3,2,4,1,2,4,4,4)
x2<-c(4,2,4,4,1,3,1,0)
cols<-c("red","red","red","red","Blue","Blue","Blue","red")
plot(x1,x2,col=cols,xlim = c(-1,5),ylim =c(-1,5) )
abline(-0.5, 1)
```

The 8th point no longer separate by the hyperplane























































